Parsing Postfix log files

### 2008-02-20 doc/logparser.tex
Documented verification of correct parsing in the coverage section.

XXX COVERAGE\@.

@@

XXX PICK A RANDOM SAMPLE OF LOG LINES AND ENSURE THEY ARE PARSED
PROPERLY\@.

@@

    \item When dealing with the complications described in
        \sectionref{complications} \sectionref{additional complications}
        the solutions are as specific and restrictive as possible, with the
        goal of minimising the number of false positives.  In addition the
        solution to the \textit{Out of order log files\/} problem described
        in \sectionref{out of order log lines} imposes conditions which
        each reassembled mail must comply with to be acceptable.

@@

Despite the lack of numerical evidence, the author is confident that the
false positive rate when reconstructing a mail is exceedingly low, if not
approaching zero.

>>>>

@@

@@

    \item When dealing with the complications described in
        \sectionref{complications} and \sectionref{additional
        complications} the solutions are as specific and restrictive as
        possible, with the goal of minimising the number of false
        positives.  In addition the solution to the \textit{Out of order
        log files\/} problem described in \sectionref{out of order log
        lines} imposes conditions which each reassembled mail must comply
        with to be acceptable.

@@

Whereas verifying by inspection that the parser correctly deals with all
60,721,709 lines in the test logs is infeasible, verifying a subset of
those logs is a tractable, if extremely time consuming, task.  A sample of
logs was obtained by randomly selecting a log file:

\verb!    perl -Mstrict -Mwarnings -MList::Util=shuffle \!\newline
\verb!            -e 'print [shuffle(@ARGV)]->[0];'!

The first 6000 lines of this log file (roughly 0.01\% of the total) was
extracted:

\verb!    sed -n -e '1,6000p' logfile > test-log-segment!

It is important that the log lines used are contiguous so that all log
entries are present for as many of the connections/mails as possible.  This
log segment was parsed with all debugging options enabled, resulting in
167,448 lines of output (27.908 lines of output per line of input).  All
167,448 lines were examined in conjunction with the input log and a dump of
the resulting database, verifying that for each of the input lines the
parser used the correct rule, executed the correct action, which in turn
produced the correct result, and inserted the correct data in the database.
The log segment produced 4 warnings, 10 mails remaining in the state
tables, and 1625 connections entered in the database.

Given the circumstantial and experimental evidence detailed above, the
author is confident that the false positive rate when reconstructing a mail
is exceedingly low, if not approaching zero.
